---
title: "RWTY"
author: "Joel Nitta"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE)
```

This script checks output of MrBayes to see if the phylogenetic analysis has been run for enough generations.

For more information about the output plots, see the RWTY [vignette](https://cran.r-project.org/web/packages/rwty/vignettes/rwty.html).

Load "RWTY" library and set number of processors (change this as needed if your machine has a different number of processors).

```{r load-package}
library(rwty)
rwty.processors <<- 4
```

Read in trees, trimming to only one per every 25 trees in the log file.

```{r load-trees}
trees <- load.multi(here::here("data/japan_pterido_rbcl_cipres/"), format = "mb", trim = 25)
```

Run RWTY analyses (makes various plots and calculates effective sample size). 

This takes ca. 2 hr 30 minutes to run with 4 processors.

```{r rwty-analysis}
# Set burnin to 25% of trees 
# = 100, since there are 10,000,000 generations with trees stored once per 1,000 generations,
# and we read in one per every 25 trees.
rbcl.rwty <- analyze.rwty(trees, burnin = 100, fill.color = 'LnL')
```

Plot different parameters.

```{r plot-output}
# - Log-Likelihood trace
rbcl.rwty$LnL.trace

# - Topology trace
rbcl.rwty$topology.trace.plot

# - Topological autocorrelation plot
rbcl.rwty$autocorr.plot

# - Treespace heatmap
rbcl.rwty$treespace.heatmap

# - Cumulative splits frequences plot
rbcl.rwty$splitfreqs.cumulative.plot
```

Check the approximate sample size (should be greater than 200).

```{r check-ess}
topological.approx.ess(trees, burnin = 100)
```
